Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
rest of intro edits

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial or temporal scales associated
with social systems.

Our examinations are motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.

>>>>

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial, or temporal scales associated
with social systems.

Our examinations are motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.
<!-- JWT: This part may have to change depending on how we do the disc -->
